My title

### 2024-03-14 paper/paper.qmd
discussion update

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Jeongwoo Kim
  - Jiwon Choi
thanks: "Code and data are available at: https://github.com/Kjeongwoo99/STA302H_Paper3"
date: today
date-format: long
abstract: "In this study, we forecasted the 2020 U.S. Presidential Election outcomes using a sophisticated statistical technique called multilevel regression with post-stratification (MRP), applied to a large-scale national survey dataset and census data. Our findings reveal how demographic factors such as age, gender, education, race, and geographic location influence voting behavior, with particular emphasis on voter preferences for Donald Trump. The analysis highlights significant variations in voter support across different states and educational backgrounds, underscoring the complex interplay of demographics in shaping electoral outcomes. This research contributes to our understanding of the American electoral landscape, demonstrating the critical role of demographic diversity in determining the direction of political preferences and election results."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
library(ggrepel)
library(maps)
library(here)
library(kableExtra)
library(statebins)
library(broom.mixed)
library(knitr)

#### Read in necessary data and model ####
cleaned_data_post_strat <-read_csv(file = here("data/analysis_data/usa_00002_cleaned.csv"), show_col_types = FALSE)
cleaned_data_survey <- read_csv(file = here("data/analysis_data/ns20191003_cleaned.csv"), show_col_types = FALSE)
survey_model <- readRDS(file = here("models/consider_trump.rds"))
prediction_model <- readRDS(file = here("models/census_data_with_predictions.rds"))
```

@@

IPUMS ("Integrated Public Use Microdata Series") is a website that offers database of samples of the American population from the American Community Surveys of 2000-present. These samples provide rich qualitative information on the long-term changes in the population. We selected the '2019 ACS' data (@citeIPUMS) as the post-stratification dataset for our research. The ACS is an ongoing survey that collects data monthly, which is then combined into 1-year, 3-year, and 5-year aggregates. It then uses stratified sampling where the U.S population is broken down into sub-groups and initial weights are assigned to each respondent.

One strength of the IPUMS survey is the fact that it provides a data with detailed demographic of the U.S. population with social, economic and housing characteristics, which is very useful in our analysis of the 2020 U.S presidential election forecast. The longitudinal data of this survey also allows researchers to analyze trends over time. The U.S. Census Bureau offers credibility of the data with high quality checks. The post-stratification process ensures correcting for sampling biases and non-response. On the other hand, since the survey relies on self-report, there lies a risk of response bias inherently. While it is an ongoing survey, there is still a time lag between the data collection and data availability. However, the large sample size, consistency and reliability of the data collection, the integrated data over time with post-stratification can justify the decision to utilize IPUMS data over other sources.

In processing the raw post-stratification dataset, which initially contained approximately 3.2 million records, we refined it down to about 2.3 million records. This was achieved through a meticulous selection process, ensuring the data's integrity and relevance for our analysis. In our analysis, we've selected the variables 'sex', 'race', 'stateicp', 'age', and 'educd' from the dataset. To simplify our analysis, respondents who indicated 'other' or provided no data for their sex have been excluded. Consequently, 'sex' has been categorized strictly as 'Male' and 'Female'. We've refined 'race' into five categories: 'White', 'Black', 'Asian', 'American Indian', and 'Other', based on the composition of the U.S. population, with White, Black, and Asian categories accounting for approximately 93 percent of the total.

The 'stateicp' variable encompasses all U.S. states, using their standard abbreviations (e.g., 'CT' for Connecticut), and extends to 55 values to include 'Puerto Rico', 'State groupings (1980 Urban/rural sample)', 'Military/Military Reservations', 'District of Columbia', and an 'State not identified' category. Age has been grouped into four categories: '18-29', '30-49', '50-64', and '70+'. For educational attainment ('educd'), we've created four categories: 'High school or less', 'Some college', 'College degree', and 'Postgrad'.

We excluded any unknown responses to ensure clarity and accuracy in categorization and to enhance clarity and align with survey data, we've renamed 'sex', 'stateicp', 'age', and 'educd' to 'gender', 'state', 'age_group', and 'education', respectively. This restructuring aims to streamline our analysis by ensuring each respondent is accurately categorized.

@fig-distribution-by-age-group, @fig-distribution-by-gender, @fig-distribution-by-race, and @fig-distribution-by-education illustrate comparisons between survey data and post-stratification data across different variables. In these visuals, orange bars represent post-stratification data, while green bars signify survey data. The percentages displayed on each figure are rounded to the nearest tenth, introducing a potential margin of error of ±0.1% in the total values. Generally, the survey data aligns closely with the post-stratification data, maintaining a discrepancy of about 10% across most categories. Notable exceptions are observed in the '30-49' age group and the 'Some college' education level, where the differences exceed this margin.

```{r}
# insert figure for state here
```

@@

```{r fig.width=10, fig.height=5}
#| echo: false
#| message: false
#| warning: false
#| label: fig-distribution-by-gender
#| fig-cap: Distribution of Sample and Population by Gender

# Calculate percentages for the survey data by gender
survey_gender <- survey_data %>%
  group_by(gender) %>%
  summarise(count = n()) %>%
  mutate(percentage = (count / sum(count)) * 100)  # Calculate percentage

# Calculate percentages for the post-strat data by gender
post_strat_gender <- post_strat_data %>%
  group_by(gender) %>%
  summarise(count = n()) %>%
  mutate(percentage = (count / sum(count)) * 100)  # Calculate percentage

# Combine the gender percentages into a single data frame for plotting
combined_gender_percentages <- rbind(
  data.frame(dataset = 'Survey', gender = survey_gender$gender, percentage = survey_gender$percentage),
  data.frame(dataset = 'Post-Strat', gender = post_strat_gender$gender, percentage = post_strat_gender$percentage)
)

# Plot the gender percentages with specified bar width and percentage on y-axis, and label each bar
ggplot(combined_gender_percentages, aes(x = gender, y = percentage, fill = dataset)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  geom_text(aes(label = sprintf("%.1f%%", percentage)),
            position = position_dodge(width = 0.8), 
            vjust = -0.3, # Adjust text position
            color = "black",
            size = 3) + 
  labs(x = "Gender", y = "Proportion", title = "Distribution of Sample and Population by Gender") +
  theme_minimal() +
  scale_fill_manual(values = c("orange", "green"))
```

```{r fig.width=10, fig.height=5}
#| echo: false
#| message: false
#| warning: false
#| label: fig-distribution-by-race
#| fig-cap: Distribution of Sample and Population by Race Ethnicity
# Read in the survey data
survey_data <- cleaned_data_survey
# Read in the post-stratification data
post_strat_data <- cleaned_data_post_strat
# Calculate percentages for the survey data by race
survey_race <- survey_data %>%
  group_by(race) %>%
  summarise(count = n()) %>%
  mutate(percentage = (count / sum(count)) * 100)  # Calculate percentage
# Calculate percentages for the post-strat data by race
post_strat_race <- post_strat_data %>%
  group_by(race) %>%
  summarise(count = n()) %>%
  mutate(percentage = (count / sum(count)) * 100)  # Calculate percentage
# Combine the race percentages into a single data frame for plotting
combined_race_percentages <- rbind(
  data.frame(dataset = 'Survey', race = survey_race$race, percentage = survey_race$percentage),
  data.frame(dataset = 'Post-Strat', race = post_strat_race$race, percentage = post_strat_race$percentage)
)
# Adjust the factor levels for the 'race' column to specify the order
combined_race_percentages$race <- factor(combined_race_percentages$race, 
                                                    levels = c("White", "Black", "Asian", "American Indian", "Other"))
# Plot the race percentages with specified bar width and percentage on y-axis, and label each bar
ggplot(combined_race_percentages, aes(x = race, y = percentage, fill = dataset)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  geom_text(aes(label = sprintf("%.1f%%", percentage)),
            position = position_dodge(width = 0.8), 
            vjust = -0.3, # Adjust text position
            color = "black",
            size = 3) + 
  labs(x = "Race", y = "Proportion", title = "Distribution of Sample and Population by Race Ethnicity") +
  theme_minimal() +
  scale_fill_manual(values = c("orange", "green"))
```

```{r fig.width=10, fig.height=5}
#| echo: false
#| message: false
#| warning: false
#| label: fig-distribution-by-education
#| fig-cap: Distribution of Sample and Population by Education
# Read in the survey data
survey_data <- cleaned_data_survey
# Read in the post-stratification data
post_strat_data <- cleaned_data_post_strat
# Calculate percentages for the survey data by education
survey_education <- survey_data %>%
  group_by(education) %>%
  summarise(count = n()) %>%
  mutate(percentage = (count / sum(count)) * 100)  # Calculate percentage
# Calculate percentages for the post-strat data by education
post_strat_education <- post_strat_data %>%
  group_by(education) %>%
  summarise(count = n()) %>%
  mutate(percentage = (count / sum(count)) * 100)  # Calculate percentage
# Combine the education percentages into a single data frame for plotting
combined_education_percentages <- rbind(
  data.frame(dataset = 'Survey', education = survey_education$education, percentage = survey_education$percentage),
  data.frame(dataset = 'Post-Strat', education = post_strat_education$education, percentage = post_strat_education$percentage)
)
# Adjust the factor levels for the 'education' column to specify the order
combined_education_percentages$education <- factor(combined_education_percentages$education, 
                                                    levels = c("High school or less", "Some college", "College degree", "Postgrad"))
# Plot the education percentages with the adjusted order
ggplot(combined_education_percentages, aes(x = education, y = percentage, fill = dataset)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  geom_text(aes(label = sprintf("%.1f%%", percentage)),
            position = position_dodge(width = 0.8), 
            vjust = -0.3, # Adjust text position
            color = "black",
            size = 3) + 
  labs(x = "Education", y = "Proportion", title = "Distribution of Sample and Population by Education") +
  theme_minimal() +
  scale_fill_manual(values = c("orange", "green"))
```

@tbl-voters-intention-to-vote-for-trump shows the proportion of voters who intend to vote for Donald Trump or not. Also, @tbl-voters-intention-of-their-primary-party shows the proportion of voters' supporting party. The data used to create these table is from the @citeSurveyData. We see that Donald Trump and his party Republican are not expected to win the popular vote before we implement the model.

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: tbl-voters-intention-to-vote-for-trump
#| tbl-cap: Voters Intention to Support Trump
data <- cleaned_data_survey

# Prepare the data with specified order
trump_counts <- data %>%
  mutate(consider_trump = factor(consider_trump, levels = c("Yes", "No", "Other"))) %>%
  count(consider_trump, name = "Number of Respondents") %>%
  mutate(`Proportion (%)` = (`Number of Respondents` / sum(`Number of Respondents`)) * 100) %>%
  mutate(`Proportion (%)` = round(`Proportion (%)`, 2)) %>%
  rename(`Response` = consider_trump)

# Use kable to create the table
kable(trump_counts, format = "latex", booktabs = TRUE, align = "c") %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position"), full_width = FALSE)
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: tbl-voters-intention-of-their-primary-party
#| tbl-cap: Voters Intention of Their Primary Party

data <- cleaned_data_survey

# Prepare the data with specified order
party_preference_counts <- data %>%
  mutate(primary_party = factor(primary_party, levels = c("Democratic", "Republican", "Other"))) %>%
  count(primary_party, name = "Number of Respondents") %>%
  mutate(`Proportion (%)` = (`Number of Respondents` / sum(`Number of Respondents`)) * 100) %>%
  mutate(`Proportion (%)` = round(`Proportion (%)`, 2)) %>%
  rename(`Party Preference` = primary_party)

# Use kable to create the table
kable(party_preference_counts, format = "latex", booktabs = TRUE, align = "c") %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position"), full_width = FALSE)
```

# Model
For our study, we employ a technique called multilevel regression with post-stratification (MRP). This approach involves creating a model based on a smaller data set, such as our survey data, and then extending the model's findings to a larger population.

The key steps in MRP involve initially selecting a dataset for model development. In this case, we utilized survey data from the Voter Study Group (@citeSurveyData). The next step is to construct a model with this smaller dataset; here, we employed logistic regression based on the survey data, formulated as seen in equation \ref{eq:logit}. Following model creation, it is then applied to a broader dataset to estimate population characteristics. For our analysis, Census data from IPUMS (@citeIPUMS) served as this larger dataset.

To predict an individual's likelihood of voting for Donald Trump, we aim to construct a logistic regression model leveraging data from the Voter Study Group (@citeSurveyData) and applying post-stratification with Census Data (@citeIPUMS). Given that logistic regression is suited for binary outcomes, we've introduced a variable, 'consider_trump', which assigns a 1 if the respondent indicates a plan to vote for Donald Trump, and a 0 for intentions to vote for other candidates, with 0 encompassing both "No" and "Other" responses.

The logistic regression model takes the form of:

\begin{equation}
log(\frac{\hat{p}}{1 - \hat{p}}) = \beta_{0} + \beta_{1}x_{sex} +
\beta_{2}x_{agegroup} + \beta_{3}x_{race} + \beta_{4}x_{state} + \beta_{5}x_{education}
\label{eq:logit}
\end{equation}

In equation \ref{eq:logit}, each $\beta$ represents a coefficient determined through regression analysis. The variables chosen for this project are sex, age, race, education, and state. These were selected because sex, age, and race are proven to be reliable indicators of voting preferences. This decision is based on patterns such as certain states consistently favoring the Republican party, while others alternate between Democratic and Republican. Education was chosen over income because it provides a clearer picture of an individual’s background than income does.

Once the logistic regression model is developed, we'll use the `predict()` function in R (@citeR) to apply our model to Census data (@citeIPUMS), breaking down the dataset into categories based on sex, race, age group, education level, and state. This will give us the likelihood of individuals within each category voting for Donald Trump. These predictions allow us to analyze potential outcomes like the popular vote winner or the electoral college vote distribution.

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: tbl-model-coefficients
#| tbl-cap: Coefficients from the Model
model <- survey_model 
coefficients <- broom.mixed::tidy(model, conf.int = TRUE)

kable(coefficients, format = "latex", booktabs = TRUE, align = "c") %>%   kable_styling(latex_options = "scale_down", font_size = 7)
```

@tbl-model-coefficients shows the estimates for the coefficients that will fit into our logistic regression equation. These coefficients will fit into Equation \ref{eq:logit}, and were calculated using data from the Voter Study Group (@citeSurveyData). The table is made using `kable` from `knitr` (@citeKnitr) and is formatted using `kableExtra` (@citekableExtra).

We use the `stan_glm()` function in R (@citeR) for our regression analysis, specifically because we are dealing with a binary outcome: whether a voter supports Donald Trump or not. The nature of our data suggests an S-shaped distribution rather than a linear one, making logistic regression a better fit than linear regression. This approach is advantageous, especially when paired with post-stratification, as it allows us to better represent under-represented groups in our analysis. For instance, despite having only 7 responses from Alaska in our survey data (@citeSurveyData), through multilevel regression and post-stratification, we can adjust this to effectively represent over 4500 individuals.

However, there are limitations to our model. The binary outcome does not allow for consideration of third-party candidates or non-voters, although this limitation is mitigated by our focus on the main candidates. More critically, our model's accuracy is heavily dependent on the quality of our survey data. Any inaccuracies or the need for adjustments in the survey can significantly impact our findings.

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-coefficient-estimates
#| fig-cap: Coefficient Estimates

coefficients %>%
  ggplot(aes(estimate, term)) + geom_point() + geom_errorbar(aes(xmin = conf.low, xmax = conf.high)) + labs(title = "Coefficient Estimates", x = "Estimate", y = "Coefficient") +   theme(axis.text.y = element_text(size = 5))
```

@fig-coefficient-estimates presents the coefficients derived from logistic regression on the survey data (@citeSurveyData). It also includes error bars, indicating the confidence interval for each coefficient estimate. In interpreting these coefficients, it's essential to understand that positive values suggest a greater likelihood of voting for Donald Trump, whereas negative values indicate a tendency to vote for other candidates, such as Joe Biden.

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: tbl-prediction-probabilities
#| tbl-cap: Example of Prediction model

# Select only the first 10 rows for the table
probability_subset <- head(prediction_model, 10)

# Create the table with kable and format with kable_styling
kable(probability_subset, format = "latex", booktabs = TRUE, align = "c") %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position"), full_width = FALSE)
```

By utilizing the results from our logistic regression model, we can formulate an equation that adheres to the structure outlined in equation \ref{eq:logit}, incorporating specific $\beta$ coefficients for each variable. Given the number of variables, detailing the equation fully is challenging. Essentially, the equation integrates the $\beta$ value of a variable if an individual's characteristic matches that variable. @tbl-prediction-probabilities offers examples of how the probability varies based on different variables.

@@

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Jeongwoo Kim
  - Jiwon Choi
thanks: "Code and data are available at: https://github.com/Kjeongwoo99/STA302H_Paper3"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(readr)
library(palmerpenguins)
library(ggrepel)
library(maps)
library(here)
library(ggplot2)
library(dplyr)
library(knitr)
library(kableExtra)
library(statebins)

#### Read in necessary data and model ####
cleaned_data_post_strat <-read_csv(file = here("data/analysis_data/usa_00002_cleaned.csv"), show_col_types = FALSE)
cleaned_data_survey <- read_csv(file = here("data/analysis_data/ns20191003_cleaned.csv"), show_col_types = FALSE)

survey_model <- readRDS(file = here("models/consider_trump.rds"))
predicton_model <- readRDS(file = here("models/census_data_with_predictions.rds"))
```

@@

IPUMS ("Integrated Public Use Microdata Series") is a website that offers database of samples of the American population from the American Community Surveys of 2000-present. These samples provide rich qualitative information on the long-term changes in the population. We selected the '' data as the post-stratification dataset for our research. The ACS is an ongoing survey that collects data monthly, which is then combined into 1-year, 3-year, and 5-year aggregates. It then uses stratified sampling where the U.S population is broken down into sub-groups and initial weights are assigned to each respondent.

One strength of the IPUMS survey is the fact that it provides a comprehensive and extensive data with detailed demographic of the U.S. population with social, economic and housing characteristics, which is very useful in our analysis of the 2020 U.S presidential election forecast. The longitudinal data of this survey also allows researchers to analyze trends over time. The U.S. Census Bureau offers credibility of the data with high quality checks. The post-stratification process ensures correcting for sampling biases and non-response. On the other hand, since the survey relies on self-report, there lies a risk of response bias inherently. While it is an ongoing survey, there is still a time lag between the data collection and data availability. However, the large sample size, consistency and reliability of the data collection, the integrated data over time with post-stratification can justify the decision to utilize IPUMS data over other sources.

The variables we have decided to use in this analysis from the dataset are 'sex', 'race', 'stateicp', 'age_group', and 'educd'. We have filtered out the respondents who have answered 'other' or no available sex data from the raw dataset for simplicity of the analysis. Therefore, 'Sex' is categorized into 'Male' and 'Female'. 'Race' is divided into 'White', 'Black', 'Asian', 'American Indian' and 'Other'. As mentioned earlier, the fact that white, black and Asian together make up around 93 percent of the U.S population, this categorization is justified. 'stateicp' is a record of all the states in the U.S. We have used the abbreviations for each state, for example, 'CT' for Connecticut, 'ME' for Maine, 'MA' for Massachusetts. We have the data of 55 states in total. 'age_group' categorized the respondents' age into four groups: '18-29', '30-49', '50-64' and '65+'. 'education' is divided into four categories: 'High school or less', 'Some college', 'College degree', 'Postgrad'. We filtered out those unknowns, and cleaned the dataset by assigning each respondent to the right category accordingly.

@@

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

@@

## Analyzing Voter Preferences Across Demographics

The analysis reveals critical insights into how education, age, race influence voting behavior. Contrary to conventional wisdom and past electoral analyses, our findings indicate a divergent pattern in voting behavior among different educational groups. The shift in party allegiance among non-college white voters from Democrats to Republicans and the nuanced preferences of voters with 'Some college' and 'Postgrad' education levels challenge the stereotypical narratives that educational attainment leads to an increase in support for the Democrats. This group, especially highly educated 'Postgrad' group being the second highest supporters suggest a reevaluation of Democrats' strategies to appeal to educated voters concerned with economic policies and national security. However, according to our data, the Republicans fail to attract voters as highest proportion of support among the four educational groups remain under 40 percent.

@tbl-voters-intention-to-vote-for-trump suggests that

shows that majority of Biden's support

The increasing propensity of older voters to lean towards the Democratic nominee, potentially driven by concerns over COVID-19 and healthcare, marks a significant shift in voting patterns. Similarly, the racial dynamics observed, with non-white demographics showing strong support for the Democratic party, reflect broader national conversations on race, immigration, and identity.

## Geographical Divides and Electoral Preferences

From @fig-distribution-by-state, we can observe that Trump leads in mid-west of America, Montana (MT), Wyoming (WY), Mississippi (MS), Maine (ME), Missouri (MO), Kentucky (KY), and Utah (UT). Even the competing states like Louisiana (LA), New Mexico (NM), Tennessee (TN) are also mid-west part of the country, which are rural areas with low population density. This is correctly estimated since in the real world as Trump won in these states: MT, WY, MS, MA, MI, KY, UT. He also won in LA and TN, which we considered were competing states. We can go more in depth of this study with the benefit of hindsight. We estimated that the biggest victory for Trump would be Montana (MT) with just below 70%. In reality, he won by 59.6%, which is lower than we thought but still sit within our error values. The next state with the highest proportion of support for Trump was Wyoming (WY) from our model with 65%, which is close to the election poll result of 69%. We were very successful with Mississippi (MS) with an estimation of 57% and the poll result of 57.5%. Maine (ME) was another very close estimate with 52% and the poll result of 53.1%. 56.8% voted for Trump in Missouri (MO), which was slightly higher than our estimation of 51%. We estimated that only 26% of voters in Hawaii (HI) would vote for Trump with error margins of +-10%, which matched 34.3% for Trump in the election. 41.9% for Trump in Colorado (CO) lie within our estimate of 37% with +-5% margins.

There were some cases where our estimation was incorrect in terms of who won the state but the results lie within our error margins. For instance, we estimated Utah (UT) in favor of the Democrats with a slight margin of 51% for Biden but Biden only received 37.6% in the election. This still lies within our error values that we estimated to be from 43% to 58%. However, there were some errors in our estimation where our model failed to predict the Trump winning in the number of states in general. Our model predicted Louisiana (LA) for Biden with 51% but he only received 39.9% of the votes. This value is lower than our error margins. 62% of the residents in Alabama, a Republican stronghold in the last eleven presidential elections had voted for Trump while our model estimated 45% of votes for Trump. The republicans won in Florida (FL) with a slight margin of 51.2% but we predicted an estimation of 45% with +-2% margins. What we estimated to be the strongest Democrat state was North Dakota (ND) with an estimation of only 23% with +-12% margins but in reality 65.1% of the residents voted for Trump.

We were able to estimate the winning of states with some success

## Weaknesses and Implications for Future Research
